---
title: "Wikipedia article quality over time"
author: "Pierce Edmiston"
output:
  html_document:
    theme: flatly
    toc: true
---

```{r, config, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  fig.path = "qualities-figs/",
  cache.path = "qualities-cache/"
)

read_chunk("qualities.R")
```

```{r, setup}
```

# Methods

```{r, data, echo = TRUE}
```

```{r, theme}
```

## Sample articles

1000 articles from the English Wikipedia were selected at random. Articles ranged in age from `r min(random1000$age)` to `r max(random1000$age)` years old.

```{r, ages, fig.width = 4, fig.height = 4}
```

## Article quality

Article quality was estimated using a machine learning algorithm trained to detect an article's quality rank, [wp10](https://meta.wikimedia.org/wiki/ORES/wp10). Articles range in quality from Stub articles to Featured Articles. The output of the wp10 model provides probabilities for each of the possible article classes. These probabilities were aggregated into a single, continuous measure of article quality.

# Results

```{r, date-mod, results = "hide"}
```

```{r, age-mod, results = "hide"}
```

```{r, quality, fig.width = 10}
```

## Models

The `date_mod` predicts article quality from the date at which the article was sampled, independent of the article's age.

```{r, date-mod, echo = 1}
```

The `age_mod` predicts article quality from the age of the article, independent of the date at which the article was sampled.

```{r, age-mod, echo = 1}
```

# Discussion

Wikipedia articles are better today than they were when they were first written. Although articles have gotten better as Wikipedia itself ages, the age of an individual article is a stronger predictor of article quality. These results support the hypothesis that Wikipedia articles incrementally improve as they accumultate edits.