---
title: "Wikipedia article quality over time"
author: "Pierce Edmiston"
output:
  html_document:
    theme: flatly
    toc: true
---

```{r, config, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.path = "figs/",
  cache.path = "cache/"
)

read_chunk("1000_random.R")
```

```{r, setup}
```

# Methods

The data used in this report is available on [github](https://github.com/evoapps/wikischolar), and can be installed using the following command: `devtools::install_github("evoapps/wikischolar", subdir = "wikischolarlib")`.

```{r, data, echo = TRUE}
```

```{r, theme}
```

## Sample articles

1000 articles from the English Wikipedia were selected at random. Articles ranged in age from `r min(random1000$age)` to `r max(random1000$age)` years old.

```{r, ages, fig.width = 4, fig.height = 4}
```

## Article quality

Article quality was estimated using a machine learning algorithm trained to detect an article's quality rank, [wp10](https://meta.wikimedia.org/wiki/ORES/wp10). Articles range in quality from Stub articles to Featured Articles. The output of the wp10 model provides probabilities for each of the possible article classes. These probabilities were aggregated into a single, continuous measure of article quality, which ranged from 1 to 6.

# Results

## Quality

```{r, date-mod, cache = TRUE, results = "hide"}
```

```{r, age-mod, cache = TRUE, results = "hide"}
```

```{r, quality, fig.width = 10}
```

The `date_mod` predicts article quality from the date at which the article was sampled, independent of the article's age.

```{r, date-mod, echo = 1}
```

The `age_mod` predicts article quality from the age of the article, independent of the date at which the article was sampled.

```{r, age-mod, echo = 1}
```

## Predictors

```{r, predictors, fig.width = 10}
```

```{r, edit-types}
```

```{r, edits-mod, cache = TRUE}
```

```{r, generations-mod, cache = TRUE}
```

```{r, cumulative-edits}
```

```{r, cumulative-generations}
```

# Discussion

As Wikipedia itself has gotten older, the average article quality has tended to increase.  Moreover, the rate of change has also increased. One possible explanation for this finding is that editors have become more efficient in their ability to make large improvements to articles. For example, automated tools used to monitor article quality may make it easier to direct editor attention to articles that are lacking in quality.

As an individual Wikipedia article ages, it also tends to improve in quality, but older articles improve less than younger articles. Although this analysis implies that article quality may asymptote at a particular age, this conclusion is only relevant to the particular measure of article quality used in this report: that of an article's quality class.

Wikipedia articles can be assigned categorical article classes that range from _Stub_ to _Featured Article_. Since _Featured Article_ is the highest obtainable class, this measure of article quality cannot by itself determine whether or not article quality has an upper limit. The alternative view is that edits to articles continue to improve article quality, however minor the improvement, indefinitely and without asymptote.
